Introduction to Causal Inference Models

### 2017-07-19 msm_introduction.Rmd
I can't figure out time-dependent example and may scrap it for now.

## Causal Estimates when A is Under the Influence of a Time-Dependent Confounder

@@

```{r time dependent std regression}
std_td_mod <- glm(Y~A0 + A1 + A0*A1, family = "gaussian", data = td_sim_data)

```

@@

```{r}
# install custom package MSModelR
# devtools::install_github("RyanGan/MSModelR")

# load library
library(MSModelR)
```

>>>>

## Causal Estimates when A is Under the Influence of a Time-Dependent Confounder
Note I can't figure out how to estimate these values yet so I may cut it out for now.

@@

```{r time dependent std regression, echo = F}
std_est_table <- as_tibble(matrix(NA, nrow = 6, ncol = 2))
colnames(std_est_table) <- c("model_params","a_estimate")

# generate a vector of formulas to estimate and fill first column
std_est_table[,1] <- formula_vector <- c("Y~A0+A1+A0*A1", "Y~A0+A1+A0*A1+Z1", 
  "Y~A0", "Y~A0+Z1", "Y~A1", "Y~A1+Z1")

# for loop to estimate standard regression estimates
for(i in 1:6){
  x <- formula_vector[i]
  mod <- lm(as.formula(x), data=td_sim_data)
  std_est_table[i,2] <- round(sum(mod$coefficients[
    # subset only A0, A1, or A0*A1
    names(mod$coefficients)=="A0" | names(mod$coefficients)=="A1" |
    names(mod$coefficients)=="A0*A1"]),1) 
}

knitr::kable(std_est_table, 
  caption = "Standard regression estimates of average effect of A on Y")
```

@@

```{r}
# install custom package MSModelR
# devtools::install_github("RyanGan/MSModelR")
# load library
library(MSModelR)

test <- g.formula(data = td_sim_data, y = "Y", a = c("A0"), model.family = "gaussian",
                  q.model = "A0+A1+A0*A1+Z1", estimate = "diff")

iptw(data=td_sim_data, y = "Y", a = "A1", w = "Z1", estimate = "diff")

?iptw
```
